### 2017-10-06 TF-vldb2018/full/sec-appendix.tex

As shown in Fig~\ref{alg-rsim}, given $P$ and ball $\ball{[v, r]}$,
\rgraphsim finds the match graph for $P$ in $\ball{[v, r]}$.
For each node $u$ in $V_{P}$, it first computes the set $\matchs(u)$ of candidate matches $w$ containing the label of $u$ (lines 1-2),
and then removes nodes from $\matchs(u)$ iteratively (lines 3-7).
A node $w$ is removed from $\matchs(u)$ if there is a adjacent node $u'$ of $u$,
but there exists no adjacent node $w'$ of $w$ such that $w'\in \matchs(u')$.
If so, \rgraphsim constructs the match graph $G_s$ \wrt the maximum match relation $\Reps$ and returns it (lines 8-10).

@@

\vspace{-1.5ex}
The satisfiability of patterns $P$ can be checked by the following algorithm:
(a) Compute the maximum match relation $\Reps$ of $P \eps P$;
(b) Check for each $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, whether $x_v \leq y_u$ holds.
One can verify that step (a) is in $O(|P|^2)$ time by invoking procedure~\ref{alg-rsim}; and step (b) can be checked in $O(|P|^2)$ time as the size of $M$ is bounded by $|P|^2$. Thus the algorithm is overall in $O(|P|^2)$ time.

@@

\vspace{-1.5ex}
(I) We firstly prove that the when the algorithm outputs ``yes", then pattern $P$ is indeed satisfiable.
This is correct since if the algorithm outputs ``yes", \ie $P \eps P$ \wrt $\Reps$ and capacity bounds in $\Reps$ are satisfied, there must exist a data graph $G$ such that $P \eeps G$.
$G$ can be derived by (i) computing equivalent classes of nodes in $P$ based on $\Reps$, such that $u$ and $w$ are in the same class iff both $(u, w)\in \Reps$ and $(w, u)\in \Reps$;
(ii) creating a set of nodes for each equivalent class, where the cardinality of the set falls in the intersection of capacity bounds on nodes in the equivalent class; and
(iii) connecting the nodes belong to two equivalent classes iff there exist edges in $P$ connecting two pattern nodes which belong to the same two equivalent classes.
We also set $r$ to be the radius of $G$. One can verify that $P \eeps G$.

\begin{figure*}[tb!]
	%\begin{widepage}
	\vspace{-1.5ex}
	\begin{center}
		\hspace{-8ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{2ex}
			\begin{center}
				\subfigure[{Unboundedness of unit data update}]{\label{fig-inc-complexity-data}
					\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
		\hspace{20ex}
		\begin{minipage}[t]{0.4\textwidth}
			%\vspace{-20.3ex}
			\begin{center}
				\subfigure[{Unboundedness of unit pattern update}]{\label{fig-inc-complexity-pattern}
					\includegraphics[scale=0.28]{./fig/inc-complexity-proof-pattern.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
	\end{center}
	\vspace{-3ex}
	%\caption{Performance evaluation of algorithm \optgrouprec for top-$k$ team formation}
	%\label{exp-semantic-effectiveness-citation}
	%\end{widepage}
	\vspace{-2.0ex}
\end{figure*}

\vspace{-1.5ex}
(II) We then prove that when the algorithm outputs ``no", then pattern $P$ is unsatisfiable.
If the algorithm outputs ``no", then either (i) $P \not\eps P$ or (ii) $P \eps P$ but capacity bounds are not satisfied.
We will prove this by contradiction.
We consider case (i) $P \not\eps P$ and assume that $P$ is satisfiable in this case.
For convenience, we use $P_1 \not\eps P_2$ to denote $P \not\eps P$, while $P_1$, $P_2$ and $P$ are exactly same.
From that $P$ is satisfiable, we know that there exists a data graph $G$ such that $P_1 \eeps G$, $P_2 \eeps G$ and $P_1 \eeps G_s$, where $G_s$ is the perfect subgraph in $G$.
By the definition of team simulation and graph simulation, from $P_2 \eeps G$, we know that $G_s \eps P_2$ holds;
from $P_1 \eeps G_s$, we know that $P_1 \eps G_s$ holds; and 
from $P_1 \eps G_s$ and  $G_s \eps P_2$, we know that $P_1 \eeps P_2$ holds.
This contradicts the assumption.
We then consider case (ii), \ie $P \eps P$ \wrt $\Reps$ while there exists $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v > y_u$, and assume that $P$ is satisfiable.
From $P$ is satisfiable, we know that there exists a data graph $G$ such that $P \eeps G$.
From $P \eps P$, we know that for any nodes $w$ in $G$, if $w$ matches with the pattern node $v$, then it must match with the pattern node $u$, that is, the number of data nodes match with $u$ is larger than that of data nodes match with $v$.
However, this contradicts that the upper bound of $u$ ($y_u$) is smaller than the lower bound of $v$ ($x_v$).

%By (I) and (II), we have proven that the algorithm is correct.

@@

We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
We know that $P\eps \ball{[v, t]}$, and suppose that $M_t$ is a binary match relation for $P$ in $\ball{[v, t]}$.
Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
there must exist a binary relation $M_r$ such that for any $(u, v) \in M_t$, where $u$ is a pattern node and $v$ is the matched data node of $u$ in $\ball{[v, t]}$, 
$(u, v) \in M_r$ holds, where $v$ is the matched data node of $u$ in $\ball{[v, r]}$, \ie $M_t \subset M_r$.
Since $M_t$ is a match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.

@@

\vspace{-2.7ex}
\begin{lemma}
	\label{lemma-innerball}
	For any data graphs $G_1$ and $G_2$, pattern graph $P$. If $G_1$ is a subgraph of $G_2$,
	then $M_1 \subset M_2$, where $M_i$ $(i=1,2)$ is the maximum match relation for $P$ in $G_i$ via graph simulation. 
\end{lemma}
\vspace{-2.5ex}

@@

\vspace{-1.3ex}
\stitle{Proofs of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
The process to compute maximum match relations for graph simulation is a recursive process to 
remove invalid matches from the initialized match relations $M$.
Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, so $(u, v)$ is removed from $M_2$.
As $G_1$ is a subgraph of $G_2$, so $(u, v)$ should also be removed from $M_1$, 
such that $(u, v) \not\in M_1$.
This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
\eop

@@

\vspace{-2ex}
\etitle{Upper bound.} We show the \NP upper bound by providing an \NP algorithm to determine whether there exists an $h$-fragmentation of $P$.\,Given $P$, the algorithm works as follows.
\looseness=-1

@@

\revise{
\vspace{-2.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

@@

	\end{center}
	\vspace{-3.0ex}
	\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
	\label{exp-semantic-effectiveness-youtube}
	%\end{widepage}
	%\vspace{-0.5ex}
\end{figure*}

>>>>

As shown in Fig~\ref{alg-rsim}, given $P$ and ball $\ball{[v, r]}$,
\rgraphsim finds the match graph for $P$ in $\ball{[v, r]}$.
For each node $u$ in $V_{P}$, it first computes the set $\matchs(u)$ of candidate matches $w$ containing the label of $u$ (lines 1-2),
and then removes nodes from $\matchs(u)$ iteratively (lines 3-7).
A node $w$ is removed from $\matchs(u)$ if there is an adjacent node $u'$ of $u$,
but there exists no adjacent node $w'$ of $w$ such that $w'\in \matchs(u')$.
If so, \rgraphsim constructs the match graph $G_s$ \wrt the maximum match relation $\Reps$ and returns it (lines 8-10).

@@

\vspace{-1.5ex}
The satisfiability of patterns $P$ can be checked by the following algorithm:
(a) Compute the maximum match relation $\Reps$ of $P \eps P$;
(b) Check for each $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, whether $x_v \leq y_u$ holds.
One can verify that step (a) is in $O(|P|^2)$ time by invoking procedure \rgraphsim; and step (b) can be checked in $O(|P|^2)$ time as the size of $M$ is bounded by $|P|^2$. Thus the algorithm is overall in $O(|P|^2)$ time.

@@

\vspace{-1.5ex}
(I) We firstly prove that when the algorithm outputs ``yes", then pattern $P$ is indeed satisfiable.
This is correct since if the algorithm outputs ``yes", \ie $P \eps P$ \wrt $\Reps$ and capacity bounds in $\Reps$ are satisfied, there must exist a data graph $G$ such that $P \eeps G$.
$G$ can be derived by (i) computing equivalent classes of nodes in $P$ based on $\Reps$, such that $u$ and $w$ are in the same class iff both $(u, w)\in \Reps$ and $(w, u)\in \Reps$;
(ii) creating a set of nodes for each equivalent class, where the cardinality of the set falls in the intersection of capacity bounds on nodes in the equivalent class; and
(iii) connecting the nodes belong to two equivalent classes iff there exist edges in $P$ connecting two pattern nodes which belong to the same two equivalent classes.
We also set $r$ to be the radius of $G$. One can verify that $P \eeps G$.

\begin{figure*}[tb!]
	%\begin{widepage}
	\vspace{-1.5ex}
	\begin{center}
		\hspace{-8ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{2ex}
			\begin{center}
				\subfigure[{Unboundedness of unit data update}]{\label{fig-inc-complexity-data}
					\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
		\hspace{20ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{-0.6ex}
			\begin{center}
				\subfigure[{Unboundedness of unit pattern update}]{\label{fig-inc-complexity-pattern}
					\includegraphics[scale=0.29]{./fig/inc-complexity-proof-pattern.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
	\end{center}
	\vspace{-3ex}
	%\caption{Performance evaluation of algorithm \optgrouprec for top-$k$ team formation}
	%\label{exp-semantic-effectiveness-citation}
	%\end{widepage}
	\vspace{-2.0ex}
\end{figure*}

\vspace{-1.5ex}
(II) We then prove that when the algorithm outputs ``no", then pattern $P$ is unsatisfiable.
If the algorithm outputs ``no", then either (i) $P \not\eps P$ or (ii) $P \eps P$ but capacity bounds are not satisfied.
We will prove this by contradiction.
We consider case (i) $P \not\eps P$ and assume that $P$ is satisfiable.
For convenience, we use $P_1 \not\eps P_2$ to denote $P \not\eps P$, while $P_1$, $P_2$ and $P$ are exactly same.
From that $P$ is satisfiable, we know that there exists a data graph $G$ such that $P_1 \eeps G$, $P_2 \eeps G$ and $P_1 \eeps G_s$, where $G_s$ is the perfect subgraph in $G$.
By the definition of team simulation and graph simulation, from $P_2 \eeps G$, we know that $G_s \eps P_2$;
from $P_1 \eeps G_s$, we know that $P_1 \eps G_s$; and 
from $P_1 \eps G_s$ and  $G_s \eps P_2$, we know that $P_1 \eps P_2$.
This contradicts the assumption.
We then consider case (ii), $P \eps P$ \wrt $\Reps$ while there exists $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, and $x_v > y_u$, and assume that $P$ is satisfiable.
From $P$ is satisfiable, we know that there exists a data graph $G$ such that $P \eeps G$.
From $P \eps P$ \wrt $\Reps$ and $(u, v)\in \Reps$, we know that for any nodes $w$ in $G$, if $w$ matches the pattern node $v$, then it must match the pattern node $u$, that is, the number of data nodes match $u$ is larger than that of data nodes match $v$.
However, this contradicts that the upper bound of $u$ ($y_u$) is smaller than the lower bound of $v$ ($x_v$).
%From (I) and (II) the correctness of the algorithm follows.

@@

We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
We know that $P\eps \ball{[v, t]}$, and suppose that $M_t$ is the maximum match relation for $P$ in $\ball{[v, t]}$.
Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
there must exist a binary relation $M_r$ such that for any $(u, v) \in M_t$, where $u$ is a pattern node and $v$ is the matched data node of $u$ in $\ball{[v, t]}$, 
$(u, v) \in M_r$ holds, where $v$ is the matched data node of $u$ in $\ball{[v, r]}$, \ie $M_t \subset M_r$.
Since $M_t$ is the maximum match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.

@@

\vspace{-2.7ex}
\begin{lemma}
	\label{lemma-innerball}
	For any data graphs $G_1$ and $G_2$, and pattern graph $P$, if $G_1$ is a subgraph of $G_2$,
	then $M_1 \subset M_2$, where $M_i$ $(i=1,2)$ is the maximum match relation for $P$ in $G_i$ via graph simulation. 
\end{lemma}
\vspace{-2.5ex}

@@

\vspace{-1.3ex}
\stitle{Proof of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
The process to compute maximum match relations for graph simulation is a recursive process to 
remove invalid matches from the initialized match relations $M$.
Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, $(u, v)$ is removed from $M_2$.
Since $G_1$ is a subgraph of $G_2$, $(u, v)$ should also be removed from $M_1$, 
such that $(u, v) \not\in M_1$.
This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
\eop

@@

\vspace{-1.5ex}
\etitle{Upper bound.} We show the \NP upper bound by providing an \NP algorithm to determine whether there exists an $h$-fragmentation of $P$.\,Given $P$, the algorithm works as follows.
\looseness=-1

@@

\revise{
\vspace{-1.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

@@

	\end{center}
	\vspace{-3.0ex}
	\caption{Performance evaluation of \optgrouprec for top-$k$ team formation problem}
	\label{exp-semantic-effectiveness-youtube}
	%\end{widepage}
	\vspace{-3.0ex}
\end{figure*}
